---
output:
  pdf_document: 
    latex_engine: xelatex
    keep_tex: false
geometry: 
  - paperwidth=8.5in
  - paperheight=11in
  - margin=0.05in 
 
header-includes:
  \usepackage{fontspec}
  \setmainfont{Arial}
  \usepackage{booktabs}
  \usepackage{colortbl}
  \usepackage{subfig}
  \usepackage{floatrow}
  \usepackage{sectsty}
  \usepackage{titlesec}
  \graphicspath{{/Users/garrettkemp/Documents/Mercer Baseball/Photos for Graphics/Sailor-Bear}}
---

```{r setup, include=FALSE}
library(tidyverse)
library(kableExtra)
library(gridExtra)
library(gtsummary)
library(pak)
library(kableExtra)
library(knitr)
library(scales)
library(pandoc)
library(ggrepel)
library(ggplot2)=
opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.pos = '!h')
```

\begin{minipage}{0.3\textwidth}
\centering
\includegraphics[width=2cm, height=2cm]{SailorBearOG}
\end{minipage}
\hfill
\begin{minipage}{0.3\textwidth}
\begin{center}
\textbf{\fontsize{20}{20}\selectfont Arm Care Report}
\end{center}
\end{minipage}
\hfill
\begin{minipage}{0.3\textwidth}
\centering
\includegraphics[width=3cm, height=2cm]{SoConLogo}
\end{minipage}

\vspace{-4mm} 
\begin{center}
\textbf{\normalsize `r params$date` `r params$pitcher`}
\end{center}

```{r, echo=FALSE, warning=FALSE, fig.width=7.8, fig.height = 3.4, fig.align='center'} 
# pitch_movement_plot
# arm_angle_plot

arm_score_plot
```
