---
output:
  pdf_document: 
    latex_engine: xelatex
    keep_tex: false
geometry: 
  - paperwidth=8.5in
  - paperheight=11in
  - margin=0.05in 
 
header-includes:
  \usepackage{fontspec}
  \setmainfont{Arial}
  \usepackage{booktabs}
  \usepackage{colortbl}
  \usepackage{subfig}
  \usepackage{floatrow}
  \usepackage{sectsty}
  \usepackage{titlesec}
  \graphicspath{{/Users/garrettkemp/Documents/Mercer Baseball/Photos for Graphics/Sailor-Bear}}
---

```{r setup, include=FALSE}
library(tidyverse)
library(kableExtra)
library(gridExtra)
library(gtsummary)
library(pak)
library(kableExtra)
library(knitr)
library(scales)
library(pandoc)
library(ggrepel)
library(ggplot2)
opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.pos = '!h')
```

\begin{minipage}{0.3\textwidth}
\centering
\includegraphics[width=2cm, height=2cm]{SailorBearOG}
\end{minipage}
\hfill
\begin{minipage}{0.3\textwidth}
\begin{center}
\textbf{\fontsize{20}{20}\selectfont Arm Care Report}
\end{center}
\end{minipage}
\hfill
\begin{minipage}{0.3\textwidth}
\centering
\includegraphics[width=3cm, height=2cm]{SoConLogo}
\end{minipage}

\vspace{-4mm} 
\begin{center}
\textbf{\fontsize{16}{16}\selectfont `r params$date` `r params$pitcher`}
\end{center}


\vspace{-3mm}
```{r, Pre Exam Stats}
Pre.Exam.Stats %>% 
  kable(format = "latex",  linesep = "", align = 'c', escape = F) %>%
  kable_styling(latex_options = "HOLD_position", position = "center", font_size = 10) %>% 
  row_spec(0, background = "#f76800", color = 'white') %>% 
  column_spec(1, border_left = T) %>% 
  column_spec(ncol(Pre.Exam.Stats), border_right = TRUE) %>% 
  add_header_above(c("Fresh - Quick Pre Exam" = 7), border_left = T, 
                   border_right = T, color = 'white', background = "#f76800") %>% 
  footnote(general = "TARM = Throwing Arm, RS = Relative Strength (Strength/Bodyweight)",
           fixed_small_size = T) %>% 
  column_spec(2, color = ifelse(Pre.Exam.Stats$`Arm Score` < 50, 'red', ifelse(Pre.Exam.Stats$`Arm Score` < 70, 'orange', 'black'))) %>% 
  column_spec(3, color = ifelse(Pre.Exam.Stats$`IRTARM RS` < .15, 'red', ifelse(Pre.Exam.Stats$`IRTARM RS` < .20, 'orange', 'black'))) %>% 
  column_spec(4, color = ifelse(Pre.Exam.Stats$`ERTARM RS` < .15, 'red', ifelse(Pre.Exam.Stats$`ERTARM RS` < .20, 'orange', 'black'))) %>% 
  column_spec(5, color = ifelse(Pre.Exam.Stats$`STARM RS` < .10, 'red', ifelse(Pre.Exam.Stats$`STARM RS` < .15, 'orange', 'black'))) %>% 
  column_spec(6, color = ifelse(Pre.Exam.Stats$`GTARM RS` < .10, 'red', ifelse(Pre.Exam.Stats$`GTARM RS` < .15, 'orange', 'black'))) %>% 
  column_spec(7, color = case_when(
    Pre.Exam.Stats$`Shoulder Balance` > 1.20 ~ 'red',
    between(Pre.Exam.Stats$`Shoulder Balance`, 1.06, 1.20) ~ 'orange',
    between(Pre.Exam.Stats$`Shoulder Balance`, .70, .84) ~ 'orange',
    Pre.Exam.Stats$`Shoulder Balance` < .70 ~ 'red',
    .default = 'black'
  ))

```

\vspace{-4mm}

```{r}
Pre.Exam.Weights %>% 
  kable(format = "latex", linesep = "", align = 'c', escape = F) %>%
  kable_styling(latex_options = "HOLD_position", position = "center", font_size = 10) %>% 
  row_spec(0, background = "#f76800", color = 'white') %>% 
  column_spec(1, border_left = T) %>% 
  column_spec(ncol(Pre.Exam.Weights), border_right = TRUE) %>% 
  add_header_above(c("Pre Exam Strength Measurements (LBS)" = 6), border_left = T, 
                   border_right = T, color = 'white', background = "#f76800")
```

\vspace{-9mm}

```{r}
Post.Exam.Weights %>%
  kable(format = "latex",  linesep = "", align = 'c', escape = F) %>%
  kable_styling(latex_options = "HOLD_position", position = "center", font_size = 10) %>% 
  row_spec(0, background = "#f76800", color = 'white') %>% 
  column_spec(1, border_left = T) %>% 
  column_spec(ncol(Post.Exam.Weights), border_right = TRUE) %>% 
  add_header_above(c("Post Exam Strength Measurements (LBS)" = 6), border_left = T, 
                   border_right = T, color = 'white', background = "#f76800")
```

\vspace{-9mm}

```{r}
Post.Exam.Losses %>% 
  kable(format = "latex",  linesep = "", align = 'c', escape = F) %>%
  kable_styling(latex_options = "HOLD_position", position = "center", font_size = 10) %>% 
  row_spec(0, background = "#f76800", color = 'white') %>% 
  column_spec(1, border_left = T) %>% 
  column_spec(ncol(Post.Exam.Losses), border_right = TRUE) %>% 
  add_header_above(c("Post Exam Strength Losses (LBS)" = 6), border_left = T, 
                   border_right = T, color = 'white', background = "#f76800")
```


```{r, echo=FALSE, warning=FALSE, fig.width=8, fig.height = 3.6, fig.align='center'} 
grid.arrange(arm_score_plot, strength_plot, ncol = 2)
```

```{r, echo=FALSE, warning=FALSE, fig.width=8, fig.height = 3.6, fig.align='center'} 
grid.arrange(ir_rom_plot, er_rom_plot, ncol = 2)
```

\newpage

\vspace{20mm}
```{r, echo=FALSE, warning=FALSE, fig.width=7.8, fig.height = 3.4, fig.align='center'} 
grid.arrange(f_rom_plot, t_arc_plot, ncol = 2)
```

